Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-01-09 Text/introduction.tex
Compared with analytics. Pretty nice coincedence.

\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage{bm}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}

@@

\subsection{Steady mass transfer}
The problem we want to address can be formulated through the following PDE:
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=0,\, C(x,0)=C_s,\, \frac{\partial C}{\partial y }(x,\delta)=0\\
&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
\end{aligned}
\feq
{\color{red} This problem is different from what I solved on computer.}

@@

@@

\section{Keeping Peclet}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.

>>>>

\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage{bm}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{leftidx}

@@

\subsection{Parabolic profile with velocity zero gradient at the wall}

@@

\subsection{The parabolic profile mass transfer and comparison}
The problem we want to address can be formulated through the following PDE:
\beq
\begin{aligned}
&\frac{\partial C}{\partial x} U(y)=D\frac{\partial^2 C}{\partial y^2}\\
&C(0,y)=0,\, C(x,\pm \delta)=C_s,\, \frac{\partial C}{\partial y }(x,0)=0\\
&U(y)=U_0 \Bigl(1-\bigl(\frac{y}{\delta}\bigr)^2\Bigr)
\end{aligned}
\feq
The same procedure can be done as in the previous case to redefine variables. After substitution
the following can be obtained:
\beq
\begin{aligned}
&\frac{\partial \Theta}{\partial \zeta}(1-\xi^2)=\frac{\partial^2 C}{\partial \xi^2}\\
\Theta(\zeta,\xi)=C-C_s\,\Theta(0,\xi)=-C_s\,\Theta(0,\pm 1)=0\\
\end{aligned}
\feq
After separation of variables, $\Theta(\zeta,\xi)=X(\zeta)Y(\xi)$ one can come up with two
equations:
\beq
\label{fourier:separation:variables}
\begin{aligned}
&\frac{\mathrm{d}X(\zeta)}{\mathrm{d}\zeta}+m^4 X(\zeta)=0\\
&\frac{\mathrm{d^2}Y(\xi)}{\mathrm{d}\xi^2}+m^4 (1-\xi^2) Y(\xi)=0
\end{aligned}
\feq
The first equation has a solution:
\beq
X(\zeta)=\exp(-m^4 \zeta)
\feq
The second equation can be simplified after substitution $\bar{\xi}=m \sqrt{2} \xi$ to the standard
equation:
\beq
Y''-\Bigl(\frac{1}{4}\xi^2+a\Bigr)Y=0.
\feq
The equation above has two solutions via parabolic cylinder functions or through the confluent
hypergeometric function \cite{abramowitz}:
\beq
\begin{aligned}
&Y_1=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{1}{4},\frac{1}{2},\frac{x^2}{2}\Bigr)\\
&Y_2=e^{-x^2/4} {_1F_1}\Bigl(\frac{a}{2}+\frac{3}{4},\frac{3}{2},\frac{x^2}{2}\Bigr)\\
\end{aligned}
\feq 
Taking symmetry conditions in the consideration by leaving only even solution, Eq.
(\ref{fourier:separation:variables}) has a solution as:
\beq
Y_m=C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 x^2\Bigr) 
\feq
To satisfy boundary condition we need to find zeros of the hypergeometric function, i.e.
${_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \Bigr)=0$. First ten eigenvalues can be
found using numerical methods, as $1.2967$, $2.3811$,$3.1093$,$3.6969$,$4.2032$,$4.6548$,$5.0662$,
$5.4467$, $5.8023$,$6.1373$. One needs to satisfy one more condition to obtain coefficients $C_m$:
\beq
-C_{s}=\sum_m{C_m e^{-m^2 x^2/2} {_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
x^2\Bigr)} 
\feq
One can multiply both parts on $(1-x^2){_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
x^2\Bigr)$ and through orthoganality Sturm-Liouiville theorem obtain coefficients:
\beq
\label{coeff:series:parabolic:profile}
C_m=-C_s \frac{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
x^2\Bigr)\mathrm{d}x}}{\int_{x=0}^{1}{(1-x^2)e^{-m^2 x^2/2}
{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2
x^2\Bigr)^2\mathrm{d}x}}
\feq
Therefore a whole solution can be written as:
\begin{equation}
C=C_{s}-C_s \sum_{m=0}{C_m e^{-m^4 \frac{x}{\delta}\frac{1}{Pe}} e^{-m^2
y^2/(2\delta^2)}{_1F_1}\Bigl(-\frac{m^2}{4}+\frac{1}{4},\frac{1}{2},m^2 \frac{y^2}{\delta^2}\Bigr)},
\end{equation}
where coefficients $C_m$ are taken from Eq. (\ref{coeff:series:parabolic:profile}). The comparison
between profiles is represented in Fig. \ref{fig:parabolic:comparison}.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/parabolic_profile_comparison.eps}
\caption{Comparison between analytical profile and simulations with pressure antibounceback
conditions. One can see given a low resolution of the profile a nice coincedence.}
\end{figure}

@@

\section{Keeping Peclet}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well.

We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.
